Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/figs/protocol.tex
Fix Fig 3 entry block + extend its caption.

\begin{document}
\begin{tikzpicture}
  \tikzset{
    title/.style={every node/.style={draw=none, font=\itshape}},
    qa/.style={circle, fill=DarkGreen, text width=5pt}
  };
  \matrix[matrix of nodes, nodes={draw, align=center, text width=3cm}, column sep=2cm, row sep=.5cm, row 1/.style=title] (A)
  {
    & OCR systems &    & NER systems &    \\
    & |(pero)| Pero OCR        &    &    &    \\
    & |(tess)| Tesseract          &   & |(cam)| CamemBERT &   \\
    |(a)| Layout \& Entry extraction &           & |[qa] (b)|  & & |[qa] (c)|  \\
    & |(kraken)| Kraken   &    & |(spacy)| Spacy       &    \\
    & |(gt)| \emph{GroundTruth}   &    &        &    \\
  };

>>>>

\begin{document}
\begin{tikzpicture}
  \tikzset{
    title/.style={every node/.style={draw=none, font=\itshape}},
    qa/.style={circle, fill=DarkGreen, text width=5pt}
  };
  \matrix[matrix of nodes, nodes={draw, align=center, text width=3cm, anchor=center}, column sep=2cm, row sep=.3cm, row 1/.style=title] (A)
  {
    & OCR systems &    & NER systems &    \\
    & |(pero)| Pero OCR        &    &    &    \\
    & |(tess)| Tesseract          &   & |(cam)| CamemBERT &   \\
    |(a)| Single-block Entry Image & |(kraken)| Kraken           & |[qa] (b)|  & & |[qa] (c)|  \\
    & |(gt)| \emph{GroundTruth}   &    & |(spacy)| Spacy       &    \\
  };
